### 2016-10-31 ms/ms.tex
added figures to ms

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for system-level
  conservation biology. Using a long-term data set comprising nearly
  20,000 pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing assembly to be punctuated
  by significant reorganizations of interactions. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, Pollinator species were opportunistic in the
  flowers they visited. Indeed, the most persistent and generalized
  species were also the most variable in their network positions. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. The sensitivity of networks to cascading
  perturbations, however, increased as the communities assembled, at
  least partially due to accumulating species richness. We elucidate
  some of the mechanisms underlying plant-pollinator network assembly
  and restoration, while providing further evidence that hedgerows are
  a valuable tool for promoting species conservation and ecosystem
  provision in agricultural areas.
\end{abstract}

@@

%% introduce mutualisms, restoration, network assembly
Global change has created a severe biodiversity crisis, and as species
are lost, so are their interactions \citep{dunn2009sixth,
  barnosky2011has}. Because mutualistic interactions are essential for
maintaining the diversity their component guilds, these systems are
particularly at risk from coextinction cascades. The nature of these
cascades will depend on the interaction patterns within a community
\citep{Memmott2004, Rezende2007, Bascompte2009, Thebault2010}. To
safeguard function it has become increasingly imperative to aid the
recovery of lost biodiversity and interactions through ecological
restoration, and a key restoration aim is to facilitate assembly of
robust interaction networks \citep{menz-2010-4}. We know little,
however, about how to re-assemble interacting communities through
restoration, or the process of ecological network assembly more
generally.

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that new species tended to interact with already well-connected
species, potentially because these species are either more abundant or
more temporally persistent. In addition, using a space-for-time
substitution to study primary succession along a glacier foreland,
\cite{albrecht2010plant} also found some evidence that assembly
occurred through preferential attachment. Network nestedness, a
pattern of interactions where a core formed by generalist species that
interact with both specialist and generalist species, increased as the
community aged \citep{albrecht2010plant}. Thus, an increase in
nestedness could result from preferential attachment process where
specialist species attach to the well-connected, generalist
core. % In addition,
% non-successional temporal dynamics also suggest a stable core of
% generalists persists despite high turnover of peripheral species
% \citep{fang2012relative, diaz2010changes, alarcon2008year}.

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
%% Lauren I love this paragraph!
In contrast to the network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or network changing points, are observed in social
networks responding to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}. In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts pollinators optimize
their use of floral resources to reduce interspecific competition and
improve resource-use efficiency \citep{pyke1984optimal,
  valdovinos2010consequences, valdovinos2013adaptive,
  albrecht2010plant, Bluthgen2007}. No studies, however, have examined
whether changing points occur during ecological network assembly, and
how these changes relate to the species behavior.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, devoto2012understanding}, suggesting
interactions are changing as the community develops. Understanding the
mechanisms of network assembly will help to guide community
restoration. Facilitating network restoration is especially imperative
in areas where species interactions provide essential ecosystem
services, such as crop pollination. In intensively managed
agricultural landscapes, the demand for pollination services is the
greatest \citep{kremen-2008-10}. However, honey bees, managed
extensively around the world to provide crop pollination, are in
global decline \citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In
addition, native pollinators, which are capable of providing
sufficient crop pollination \citep{kremen-2002-16816,
  winfree-2007-1105, kremen-2004-1109}, are in short supply because
these landscapes make poor habitats for pollinator populations
\citep{kremen-2002-16816}. To ensure the continued provision of
ecosystem services and curb biodiversity loss, it is critical to
restore pollinators and their interactions in agricultural
landscapes. To promote pollinator services in agriculture, farmers may
chose to plant strips of native plants along farm edges (hedgerows) to
help provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, mgonigle-2015-x, kremen-2015-602,
  ponisio2015farm}. In addition, hedgerows promote the persistence and
colonization of floral resource specialists
\citep{mgonigle-2015-x}. It is important to further understand how
these new species are being incorporated into the network as the
community assembles, or the consequences for interaction patterns and
robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator communities assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a build
up of interactions as would be predicted by preferential attachment,
or punctuated by significant reorganizations of interactions (i.e.,
network changing points). Even with changing points in interaction
organization, networks could still be assembling via preferential
attachment if the network reorganizations were primarily driven the by
peripheral, temporally variable species while a stable, well-connected
core of species persist. We test whether the species that are most
variable in their network position --- and thus important contributors
to network reorganizations --- are less persistent and connected
species. To further explore the mechanisms underlying the temporal
dynamics of the networks, we examine patterns in the species and
interaction temporal turnover. Lastly, we investigate whether networks
are assembling toward predictable interaction patterns, and the
ramifications for the robustness of the networks to species extinction
and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of independent
assembling hedgerows communities (N=5), as well as in two types of
non-assembling communities to serve as controls: unrestored, weedy
field margins (N=19) and mature hedgerows (greater than 10 years since
planting, N=29). The sites were located in the Central Valley of
California in Yolo, Colusa and Solano Counties. This area is composed
of intensively managed agriculture --- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows we planted
along field margins where they do not remove valuable land from
production. Plantings are between are ca.~3--6 m wide and
approximately 350 m long, bordering large (ca.\ 30--hectare) crop
fields. Hedgerows consist of native, perennial, shrub and tree
plantings including \textit{Rosa californica}, \textit{Cercis
  occidentalis}, \textit{Ceanothus spp.}, \textit{Heteromeles
  arbutifolia}, \textit{Sambucus mexicana}, \textit{Eriogonum spp.},
\textit{Baccharis spp.}, \textit{Salvia spp}. and others
\citep[Fig.~S1][]{menz-2010-4, kremen-2015-602, mgonigle-2015-x}. The
mean distance between monitoring sites was $15$ km, and the minimum
distance between sites of the same type sampled in the same year was 2
km.  The entire area surveyed spanned almost $300$ km$^2$. The crop
fields adjacent to all sites were similarly managed as intensive,
high-input monoculture.

Monitoring began in 2006 and continued through 2014. Surveys of the
assembling hedgerows began the year before the area was restored. For
logistical reasons, no sampling of assembling hedgerows was conducted
in 2010. Sites were sampled between two and five times per year
(Tables S1-S3). In each round of sampling, the order in which sites
were sampled was randomized. Surveys were conducted under sunny
conditions when the temperature was above $21^{\circ}\mathrm{C}$ and
wind speed was below $2.5$ meters/second.

@@

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental reorganizations in large-scale interaction
patterns. A change point is caused by a merge, split, fragmentation or
formation of modules (also called compartments). Change point
detection methods have yet to be generalized to quantitative networks,
so for this analysis we focused on qualitative (binary)
networks. Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative structure patterns at all
scales in the network \citep{peel2014detecting}. A network $G$ is
composed of vertices $V$ and edges $E$. The GHRG model decomposes the
$N$ vertices into a series of nested groups, the relationships among
which are represented by the dendrogram $T$. The tips of $T$ are the
vertices of $G$, and the probability that two vertices $u$ and $v$
connect is given by the parameter $p_r$. The probability distribution
of the network $G$ thus defined as:

@@

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we compare the fit of two models --- one where a change point
occurred between two networks, and one where no change occurred ---
using posterior Bayes factors. We chose a sliding window of length,
$w$, of four, within which to find change points. Larger windows allow
for more gradual changes, and four was the maximum possible with our
maximum of eight years of data. Lastly, to calculate a $p$-value for
the Bayes factors, we use parametric bootstrapping to numerically
estimate the null distribution \citep{peel2014detecting}. We employed
code published online by L.~Peel for the change point
analysis. Analyses were conducted in Python 3.4.

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trails, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type. We used
standard techniques to determine whether the assumptions of the models
were met for this and all subsequent models. For the non-assembling
hedgerows and weedy field margins, only sites with five or greater
survey years were included in this analysis (N=11). All statistical
analysis were conducted in R 3.2.3 \citep{R}.

@@

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality describes the centrality of a
species in the network by calculating path lengths to other vertices
(species) in the graph \citep{freeman1978centrality}. The shorter the
mean path length to other species, the higher is the closeness
centrality. We use linear mixed models to test whether the species
closeness variability (log) is related to the persistence or degree of
that species \citep{lme4, lmetest}. We included random effects for
species, as well as site. Because the degree and persistence of
pollinators were strongly correlated, ($\rho = 0.84$, $p$-value $<$
$2*10^{-16}$), we include each explanatory variable in the model
separately. Plant degree and persistence were not significantly
correlated, but we use the same models as we did for the pollinators
for consistency. An approximately logarithmic increase in closeness
centrality, as would be expected with assembly by preferential
attachment, would also lead to a high variability in closeness scores,
so we test whether log closeness centrality increases through time.

@@

%%Lauren I really liked the way you explained this part =]
Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. For example, assembling networks may
have higher rates of pollinator turnover than non-assembling
communities because new pollinator species are colonizing and
establishing themselves \citep{mgonigle-2015-x}. Similarly, if
pollinators try to maximize their foraging efficiency based on the
species present, interactions may turnover more quickly than in
established communities. In addition, at assembling hedgerows,
unvisited plants may appear to ``colonize'' the networks as they
establish new interactions with pollinators.

To estimate the temporal species and interaction turnover, we use an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, however, we estimated turnover across years at a site. We
first calculated the pairwise dissimilarity of plants, pollinators and
interactions between years within each site using the Chao
dissimilarity estimator that incorporates abundances, while also
accounting for unobserved records \citep{chao-2005-148}. Dissimilarity
estimates can be affected by the total number of species and
individuals sampled at a site \citep[e.g.,][]{ponisio2015farm}. For
example, the probability that two sites do not share any species is
higher when there are few individuals at those sites. Following
\cite{ponisio2015farm}, we use null models that constrained species
richness to estimate the deviation of the observed dissimilarity from
that, which would be expected under a random community assembly
process. With the corrected dissimilarity values, we then calculated
the multivariate dispersion of community composition across years
\citep{anderson-2011-19}. In order to test whether assembling
hedgerows had more species and interactions turnover than
non-assembling communities, the species and interaction temporal
turnover estimates were included as response variables in a linear
mixed model with site type as an explanatory variable along with site
as a random effect \citep{lme4, lmetest}.

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~\ref{fig:methods}). We develop a method to examine the temporal
turnover of interactions with weightings based on their similarity. We
followed \cite{ahn2010link} algorithm to hierarchically cluster all
the interactions (edges) across sites and years based on their
similarity, and build a dendrogram. The interaction similarity is
based how may plants and pollinators (vertices) two edges share
\citep{ahn2010link, kalinka2011linkcomm}. The more species edges
shared in common, the shorter the branch length between them on the
dendrogram.  We next calculated the temporal turnover of interactions
weighted by their similarity, as approximated by ``phylogenetic''
distance \citep{graham2008phylogenetic, picante-2010-1463}. When then
use linear models to test whether the weighted turnover of
interactions varied between assembling and non-assembling networks
\citep{lme4, lmetest}.

@@

To test whether network modularity, nestedness, connectance or
specialization changed linearly with assembly, we use linear mixed
models with the descriptive network metrics as the response variable,
year of assembly as the explanatory variable, and random effects of
site and year. The number of species in a network affects affects the
patterns of interaction possible, so we also examined the change in
plant and pollinator species richness through time. We employ
generalized linear mixed models with Poisson error to model
richness. We scaled explanatory variables.

\subsection*{Network robustness}
Lastly, we test whether the changes in interaction patterns associated
with network assembly affect the robustness of the network to species
loss and cascading perturbations. Following \cite{Memmott2004}, we
simulate plant species extinction and the subsequent extinction
cascades of pollinator species. Because the reproduction of plant
species if facilitated by active restoration efforts, it is unlikely
the extinction of pollinator species would affect plant populations in
the hedgerows. However, plants ceasing to bloom, for example in
response to drought, will likely affect the pollinators that depend on
them. We eliminate plants species based on their degree or abundance,
and then calculate the number of pollinators that secondarily went
extinct. The area below the extinction curve is an estimate of network
robustness \citep{Memmott2004, bipartite}.

We also explored how the robustness to cascading perturbations changed
as community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization}, and has implications to
how integrated is the dynamics of the elements of the networks
\citep{gibert2013spatial}. The larger the algebraic connectivity, the
more robust a network is to cascading perturbations, and the easier it
is to break the community into isolated groups of species (Gaiarsa et
al., submitted).

@@

The majority ($76\%$) of the sites underwent at least one significant
interaction reorganization (Fig.~\ref{fig:changePoints},
\ref{fig:changePoints2}).  All five of the assembling hedgerows
experienced network changing points, whereas only $40\%$ and $81\%$ of
non-assembling hedgerows and field margins, respectively, underwent
significant interaction reorganizations. Assembling hedgerows had
significantly more changing points than the non-assembling networks
(estimate of the difference in the odds ratios between assembling and
non-assembling networks, $3.316$, $95\%$ CI $[1.314, 8.572]$,
$p$-value= $0.0117$). Network assembly following restoration is thus
punctuated by more interaction reorganizations than would be expected
by environmental shifts alone that would effect assembling and
non-assembling networks equally.

@@

Both plant and pollinator species richness increased through time
(Fig.~\ref{fig:baci}, estimate of the slope of richness through time
$\pm$ SE, pollinators: $0.193$ $\pm$ $0.0729$, $p$-value=$0.008$;
plants: $0.212$ $\pm$ $0.0653$, $p$-value=$0.001$). Unsurprisingly,
pollinator species are colonizing and persisting at the assembling
hedgerows. Plant species richness is based on the flowers actually
visited by pollinators and not the presence of a particular plant
species at a site. Thus, though some new plant species may establish
themselves in the hedgerows, the increase in plant richness in the
networks is likely due to plants attracting visitors, as they offer
better rewards.

>>>>

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a long-term data set comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, pollinator species were opportunistic in the
  flowers they visited. The most persistent and generalized species
  were also the most variable in their network positions. High species
  and interaction turnover was ubiquitous across assembling and
  non-assembling communities, though unique interactions turned over
  at higher rates in assembling hedgerows as the networks continually
  reorganized. Nestedness of assembling networks also increased
  through time, but there was no increase in robustness to simulated
  plant extinctions. The sensitivity of networks to cascading
  perturbations, however, increased as the communities assembled, at
  least partially due to accumulating species richness. We elucidate
  some of the mechanisms underlying plant-pollinator network assembly
  and restoration, while providing further evidence that hedgerows are
  a valuable tool for promoting species conservation and ecosystem
  service? provision in agricultural areas.
\end{abstract}

@@

%% introduce mutualisms, restoration, network assembly
Global change has created a severe biodiversity crisis, and as species
are lost, so are their interactions \citep{dunn2009sixth,
  barnosky2011has}. Because mutualistic interactions are essential for
maintaining the diversity of their component guilds, these systems are
particularly at risk from coextinction cascades. The nature of these
cascades will depend on the interaction patterns within a community
\citep{Memmott2004, Rezende2007, Bascompte2009, Thebault2010}. To
safeguard ecological function, it has become increasingly imperative
to aid the recovery of lost interactions and component biodviersity
through ecological restoration, and a key restoration aim is to
facilitate assembly of robust interaction networks
\citep{menz-2010-4}. We know little, however, about how to re-assemble
interacting communities through restoration, or the process of
ecological network assembly more generally.

%% most people think network assemble via preferential attachment, and
%% there is some evidence of that. (other studies on mutualisms?)
Preferential attachment, the most widely explored mechanism of network
assembly, \citep{barabasi1999emergence}, predicts that species
entering a network are more likely to interact with species that are
already well-connected \citep[''the rich-get-richer''
principle,][]{barabasi1999emergence}. In pollination systems --- a
particularly ubiquitous mutualism \citep{ollerton-2011-321,
  klein-2007-303} --- some studies have found support for this
assembly mechanism. Investigating the day-to-day, temporal assembly of
a plant-pollinator network within a season, \cite{Olesen2008} found
that phenologically new plant and pollinator species tended to
interact with already well-connected species, potentially because
these species are either more abundant or more temporally
persistent. In addition, using a space-for-time substitution to study
primary succession along a glacier foreland, \cite{albrecht2010plant}
also found some evidence that assembly occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}.  An
increase in nestedness could result from the preferential attachment
process where specialist species attach to the well-connected,
generalist core.

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
%% Lauren I love this paragraph!
In contrast to the network build-up described by preferential
attachment, significant reorganizations of interactions can punctuate
assembly \citep{peel2014detecting}. Such significant reorganizations
of interactions, or network changing points, are observed in social
networks that respond to abrupt shifts in the behavior of interactors
\citep{peel2014detecting}. In ecological communities, such shifts may
occur if, as new species colonize, resident species change their
interaction partners to optimize their foraging effort. In
plant-pollinator communities, theory predicts that pollinators
optimize their use of floral resources to reduce interspecific
competition and improve resource-use efficiency
\citep{pyke1984optimal, valdovinos2010consequences,
  valdovinos2013adaptive, albrecht2010plant, Bluthgen2007}. No
studies, however, have examined whether network changing points occur
during ecological network assembly, and how these changes relate to
the species behavior.

%% restoration
Understanding network assembly is particularly relevant to ecological
restoration, which is essentially 'applied succession'
\citep[e.g.,][]{parker1997scale}. In pollination systems, the time
since an area was restored has been shown to affect the structure of
networks \citep{forup-2008-742, devoto2012understanding}, suggesting
interactions are changing as the community develops. Understanding the
mechanisms of network assembly will help to guide community
restoration. Facilitating network restoration is especially imperative
in areas where species interactions provide essential ecosystem
services, such as crop pollination. To ensure the continued provision
of ecosystem services and curb biodiversity loss, it is critical to
restore pollinators and their interactions in agricultural
landscapes. To promote pollinator services in agriculture, farmers may
chose to plant strips of native plants along farm edges (hedgerows) to
help provide habitat for pollinators without removing arable land from
production. Hedgerows augment the richness, abundance and trait
diversity of pollinators in agricultural landscapes
\citep{morandin-2013-829, kremen-2015-602, ponisio2015farm}, and
promote the persistence and colonization of floral resource
specialists \citep{mgonigle-2015-x}. It is important to understand how
these new species are being incorporated into the network as the
community assembles, and the consequences for interaction patterns and
robustness.

%% Lauren I would put 10 year dataset; and I *loved* the way you
%% organized the ideas here!!
We explore the process of network development using a nine year
dataset of plant-pollinator community assembly following hedgerow
restoration in the highly simplified and intensively managed
agricultural landscape of California's Central Valley.  We first
determine whether the mechanism underlying network assembly is a build
up of interactions as would be predicted by preferential attachment,
or instead is punctuated by significant reorganizations of
interactions (i.e., network changing points). Even with changing
points in interaction organization, networks could still be assembling
via preferential attachment if the network reorganizations were
primarily driven by peripheral, temporally variable species while a
stable, well-connected core of species persist. We test whether the
species that are most variable in their network position --- and thus
important contributors to network reorganizations --- are less
persistent and connected species. To further explore the mechanisms
underlying the temporal dynamics of the networks, we examine patterns
in the species and interaction temporal turnover. Lastly, we
investigate whether networks are assembling toward predictable
interaction patterns, and the ramifications for the robustness of the
networks to species extinction and cascading perturbations.

@@

We surveyed plant-pollinator interaction networks of independent
assembling hedgerows communities (N=5), and of two types of
non-assembling communities to serve as controls: unrestored, weedy
field margins (N=19) and mature hedgerows (greater than 10 years since
planting, N=29). The sites were located in the Central Valley of
California in Yolo, Colusa and Solano Counties. This area is composed
of intensively managed agriculture --- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows are ca.~3--6
m wide and approximately 350 m long, bordering large (ca.\
30--hectare) crop fields. Hedgerows consist of native, perennial,
shrub and tree plantings including \textit{Rosa californica},
\textit{Cercis occidentalis}, \textit{Ceanothus spp.},
\textit{Heteromeles arbutifolia}, \textit{Sambucus mexicana},
\textit{Eriogonum spp.}, \textit{Baccharis spp.}, \textit{Salvia
  spp}. and others \citep[Fig.~S1][]{menz-2010-4, kremen-2015-602,
  mgonigle-2015-x}. The mean distance between monitoring sites was
$15$ km, and the minimum distance between sites sampled in the same
year was 1 km.  The entire area surveyed spanned almost $300$
km$^2$. The crop fields adjacent to all sites were similarly managed
as intensive, high-input monoculture.

Monitoring of assembling hedgerows began in 2006 and continued through
2014. Surveys of these sites began the year before the area was
restored. For logistical reasons, no sampling of assembling hedgerows
was conducted in 2010. Sites were sampled between two and five times
per year (Tables S1-S3, mean $3.4$ samples per year). In each round of
sampling, the order in which sites were sampled was
randomized. Surveys were conducted under sunny conditions when the
temperature was above $21^{\circ}\mathrm{C}$ and wind speed was below
$2.5$ meters/second.

@@

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}
We employed a change point detection method \citep{peel2014detecting}
to identify fundamental reorganizations in large-scale interaction
patterns. A change point is caused by a merge, split, fragmentation or
formation of modules (also called compartments). Change point
detection methods have yet to be generalized to quantitative networks,
so for this analysis we focused on qualitative (binary)
networks. Following \cite{peel2014detecting}, we first defined a
probability distribution over the networks using the generalized
hierarchical random graph model (GHRG). The GHRG model is able to
capture both assortative and disassortative structure patterns at all
scales in the network \citep{peel2014detecting}. A network $G$ is
composed of vertices $V$ and edges $E$. The GHRG model decomposes the
$N$ vertices into a series of nested groups, the relationships among
which are represented by the dendrogram $T$. The tips of $T$ are the
vertices of $G$, and the probability that two vertices $u$ and $v$
connect is given by the parameter $p_r$. The probability distribution
of the network $G$ is thus defined as:

@@

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we use Bayes factors to compare the fit of two models --- one
where a change point occurred between two networks, and one where no
change occurred. We chose a sliding window of length, $w$, of four,
within which to find change points. Larger windows allow for more
gradual changes, and four was the maximum possible with our eight
years of data. Lastly, to calculate a $p$-value for the Bayes factors,
we use parametric bootstrapping to numerically estimate the null
distribution \citep{peel2014detecting}. We employed code published
online by L.~Peel for the change point analysis. Analyses were
conducted in Python 3.4.

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trials, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type. We used
standard techniques to determine whether the assumptions of the models
were met for this and all subsequent models. For the non-assembling
hedgerows and weedy field margins, only sites with five or greater
survey years were included in this analysis (N=11). All statistical
analyses were conducted in R 3.2.3 \citep{R}.

@@

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality represents the importance of a
space by calcuating the path lengths to other vertices (species) in
the network \citep{freeman1978centrality}. The shorter the mean path
length to other species, the higher is the closeness centrality. We
use linear mixed models to test whether the species closeness
variability (log) is related to the persistence or degree of that
species \citep{lme4, lmetest}. We included random effects for species
and site. Because the degree and persistence of pollinators were
strongly correlated, ($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), we
include each explanatory variable in separate models. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency.  Because an
approximately logarithmic increase in closeness centrality, as would
be expected with assembly by preferential attachment, would also lead
to high variability in closeness scores, we also test whether log
closeness centrality increases through time.

@@

%%Lauren I really liked the way you explained this part =]
Reorganizations of network structure can be the result of species
turnover or species changing their interaction partners (i.e.,
re-wiring). To better understand the mechanisms underlying the
temporal dynamics of the assembling networks, we examined patterns of
species and interaction turnover. For example, assembling networks may
have higher rates of pollinator turnover than non-assembling
communities because new pollinator species are colonizing and
establishing themselves \citep{mgonigle-2015-x}. Similarly, because
species are turning over and pollinators are trying to maximize their
foraging efficiency based on the species present, interactions may
turnover more quickly than in established communities. In addition, at
assembling hedgerows, plants that are unvisited in early years may
appear to ``colonize'' the networks as they became more attractive
resources and establish new interactions with pollinators.

To estimate the temporal species and interaction turnover, we use an
approach similar to calculating spatial $\beta$-diversity. Instead of
calculating the variation in community composition across sites within
a year, we estimated turnover across years at a site. We first
calculated the pairwise dissimilarity of plants, pollinators and
interactions between years within each site using the Chao
dissimilarity estimator that incorporates abundances, while also
accounting for unobserved records \citep{chao-2005-148}. Dissimilarity
estimates can be affected by the total number of species and
individuals sampled at a site \citep[e.g.,][]{ponisio2015farm}. For
example, the probability that two sites do not share any species is
higher when there are few individuals at those sites. Following
\cite{ponisio2015farm}, we use null models that constrained species
richness to estimate the deviation of the observed dissimilarity from
that which would be expected under a random community assembly
process. With the corrected dissimilarity values, we then calculated
the multivariate dispersion of community composition across years
\citep{anderson-2011-19}. In order to test whether assembling
hedgerows had more species and interactions turnover than
non-assembling communities, the species and interaction temporal
turnover estimates were modeled as responses in a linear mixed model
with site type as an explanatory variable and site as a random effect
\citep{lme4, lmetest}.

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, occupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~\ref{fig:methods}). We develop a method to examine the temporal
turnover of interactions with weightings based on their similarity. We
followed the algorithm of \cite{ahn2010link} to cluster all the
interactions (edges) hierarchically across sites and years based on
their similarity, and build a dendrogram. The interaction similarity
is based how may plants and pollinators (vertices) two edges share
\citep{ahn2010link, kalinka2011linkcomm}. The more species edges
shared in common, the shorter the branch length between them on the
dendrogram.  We next calculated the temporal turnover of interactions
weighted by their similarity, as approximated by ``phylogenetic''
distance \citep{graham2008phylogenetic, picante-2010-1463}. We then
use linear models to test whether the weighted turnover of
interactions varied between assembling and non-assembling networks
\citep{lme4, lmetest}.

@@

To test whether network modularity, nestedness, connectance or
specialization changed linearly with assembly, we used linear mixed
models with the descriptive network metrics as the response variable,
year of assembly as the explanatory variable, and random effects of
site and year. The number of species in a network affects the patterns
of interaction possible, so we also examined the change in plant and
pollinator species richness through time. We employ generalized linear
mixed models with Poisson error to model richness. We scaled
explanatory variables.

\subsection*{Network robustness}
Lastly, we tested whether the changes in interaction patterns
associated with network assembly affect the robustness of the network
to species loss and cascading perturbations. Following
\cite{Memmott2004}, we simulated plant species extinction and the
subsequent extinction cascades of pollinator species. Because the
reproduction of plant species is facilitated by active restoration
efforts, it is unlikely the extinction of pollinator species would
affect plant populations in the hedgerows. However, plants ceasing to
bloom, for example in response to drought, will likely affect the
pollinators that depend on them. We eliminated plants species based on
their degree or abundance, and then calculated the number of
pollinators that secondarily went extinct. The area below the
extinction curve is an estimate of network robustness
\citep{Memmott2004, bipartite}.

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., in prep). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization, gibert2013spatial}. The
larger the algebraic connectivity, the more sensitive a network is to
cascading perturbations. Perturbations can have negative consequences
for the species in the network such as the decrease in abundance of a
plant or pollinator. For example, a pollinator could decrease in
abundance, and the pollination services it provided to the plants it
visited would be diminished. The effected plants would set less seeds,
and decrease in abundance the subsequent year. The pollinators that
depended on those plant species would suffer, and the cascade would
continue to propagate throughout the network. A perturbation could
have a positive effect, like the increase in abundance of a
species. Similar to the negative perturbation, the impact of the
positive perturbation would cascade through the network. The examples
of negative perturbations (e.g., resource collapse, disease,
parasites), however, outnumber possible positive perturbations. Both
of these metrics of network resilience are static --- they do not
account for the ability of species to alter their interaction
depending on circumstances.

@@

The majority ($76\%$) of the sites underwent at least one significant
interaction reorganization (Fig.~\ref{fig:changePoints},
\ref{fig:changePoints2}).  All five of the assembling hedgerows
experienced network changing points, whereas only $40\%$ and $81\%$ of
non-assembling hedgerows and field margins, respectively, underwent
significant interaction reorganizations. Assembling hedgerows had
significantly more changing points than the non-assembling networks
(estimate of the difference in the odds ratios between assembling and
non-assembling networks, $3.316$, $95\%$ CI $[1.314, 8.572]$,
$p$-value= $0.0117$). Network assembly following restoration is thus
punctuated by more interaction reorganizations than would be expected
by environmental shifts alone that would effect all networks
similarly.

@@

Both plant and pollinator species richness increased through time
(Fig.~\ref{fig:baci}, estimate of the slope of richness through time
$\pm$ SE, pollinators: $0.193$ $\pm$ $0.0729$, $p$-value=$0.008$;
plants: $0.212$ $\pm$ $0.0653$, $p$-value=$0.001$). Unsurprisingly,
pollinator species are colonizing and persisting at the assembling
hedgerows. Plant species richness in the networks is based on the
flowers actually visited by pollinators and not the presence of a
particular plant species at a site. Thus, though some new plant
species may establish themselves in the hedgerows, the increase in
plant richness in the networks is likely due to previously unvisited
plants attracting visitors as they mature and offer better rewards.
